Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics

### 2020-08-12 infiniteci.tex
Updates from Overleaf

%% LyX 2.3.4.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

@@

\begin{document}
\title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
\author{Jonas Moss \orcid{0000-0002-6876-6964}\\
Department of Mathematics, University of Oslo\\
PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
\emph{jonasmgj@math.uio.no}}
\maketitle
\begin{abstract}
Meta-analysis, the statistical analysis of results from separate studies,
is a fundamental building block of science. But the assumptions of
classical meta-analysis models are not satisfied whenever publication
bias is present, which causes inconsistent parameter estimates. Hedges'
selection function model takes publication bias into account, but
estimating and infering with this model is tough. Using a generalized
Gleser--Hwang theorem, we show there is no confidence set of guaranteed
finite diameter for the parameters of Hedges' selection model. This
result provides a partial explanation for why inference with Hedges'
selection model is fraught with difficulties.
\end{abstract}
\keywords{meta-analysis \and confidence intervals \and file-drawer  problem \and publication bias \and selection models \and weigth function models}

>>>>

%% LyX 2.3.4.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twoside]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

@@

%% almost as usual
\author{Matthias Templ\\ Vienna University of Technology \And 
        Second Author\\ Affiliation}
%% \AND can be used instead of \And and starts a new line
\title{Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Templ, Second Author} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
\Shorttitle{A Capitalized Title} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
  This guideline of the Austrian Journal of Statistics (AJS) shows the required style of manuscripts submitted to the Austrian Journal of Statistics. We highly recommend
to follow exactly the provided instructions already at the very
beginning when writing the paper. The present document can be used
directly as template. The file named {\tt guidelinesAJS.tex} may be
obtained from the site \href{https://github.com/matthias-da/ajs-public}{https://github.com/matthias-da/ajs-public}.

Manuscripts submitted without considering the AJS style file will be very likely not sent into review, but declined with possibility for re-submission.
}
\Keywords{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}
\Plainkeyword{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}

%% publication information
%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{2012-06-04}
%% \Acceptdate{2012-06-04}
%% \setcounter{page}{1}
\Pages{1--xx}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Matthias Templ\\
  Institue of Data Analysis and Process Design\\
  Zurich University of Applied Sciences\\
  CH-8400 Winterthur, Switzerland\\
  E-mail: \email{matthias.templ@gmail.com}\\
  URL: \url{https://www.zhaw.ch/de/ueber-uns/person/teml/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

%% for those who use Sweave please include the following line (with % symbols):
%% need no \usepackage{Sweave.sty}

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Infinite Diameter Confidence Sets in Hedges' Publication Bias Model}
\author{Jonas Moss \orcid{0000-0002-6876-6964}\\
Department of Mathematics, University of Oslo\\
PB 1053, Blindern, NO-0316, Oslo, Norway\emph{}\\
\emph{jonasmgj@math.uio.no}}
\maketitle
\begin{abstract}
Meta-analysis, the statistical analysis of results from separate studies,
is a fundamental building block of science. But the assumptions of
classical meta-analysis models are not satisfied whenever publication
bias is present, which causes inconsistent parameter estimates. Hedges'
selection function model takes publication bias into account, but
estimating and inferring with this model is tough. Using a generalized
Gleser--Hwang theorem, we show there is no confidence set of guaranteed
finite diameter for the parameters of Hedges' selection model. This
result provides a partial explanation for why inference with Hedges'
selection model is fraught with difficulties.
\end{abstract}
\keywords{meta-analysis \and confidence intervals \and file-drawer  problem \and publication bias \and selection models \and weigth function models}
